### 2008-12-20 talk/ecoop2009/jitgen.tex
fix one of the last XXXs

\anto{maybe we should at least mention promotion, and refer to the proper
  section for details?}

>>>>

There are cases in which having a green variable is essential for generating
good code, but it is not possible to use the \texttt{concrete} due to an
unsatisfiable dependency: Section~\ref{sec:promotion} introduces
\emph{promotion}, the novel technique that makes possible to solve this
problem.
